Weakly Nonlinear MRI: Notes

### 2014-04-07 notes/mri_notes.tex
symmetry. I hope this makes sense

%% Graphics and math
\usepackage{graphics,graphicx,subfigure}
\usepackage{amsmath}
\usepackage{amsfonts}

@@

>>>>

%% Graphics and math
\usepackage{graphics,graphicx,subfigure}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[makeroom]{cancel}

@@

Because the inner product integrations are actually performed over both z and x, the even/oddness of the fluid quantity eigenfunctions can force the inner product to be zero. Thus for the solvability condition: \\

 $\left< \mathbf{V}^\dagger \cdot \widetilde{\mathcal{L}}_1 \partial_Z \mathbf{V_1}\right> = 0 $ \\

 $\left< \left(\mathbb{V}^\dagger e^{iQz} + c.c.\right) \cdot \left(\widetilde{\mathcal{L}}_1 \partial_Z \alpha(T, Z) \mathbb{V}_{11} e^{i Q z} + c.c. + \widetilde{\mathcal{L}}_1 \partial_Z \beta(T, Z)\mathbb{U}_{11}\right) \right> = 0$ \\

 $\iint \mathbb{V}^\dagger e^{iQz} \cdot \widetilde{\mathcal{L}}_1 \partial_Z \alpha(T, Z)^* \mathbb{V}_{11}^* e^{-i Q z^*} \, dx dz \, + \, \cancel{\iint \mathbb{V}^\dagger e^{iQz} \cdot \widetilde{\mathcal{L}}_1 \partial_Z \alpha(T, Z) \mathbb{V}_{11} e^{i Q z} \, dx dz} \, + $ \\
$\cancel{\iint \mathbb{V}^\dagger e^{iQz} \cdot \widetilde{\mathcal{L}}_1 \partial_Z \beta(T, Z)^*\mathbb{U}_{11}^* \, dx dz} \, + \, \cancel{\iint {\mathbb{V}^\dagger}^* e^{-iQz^*} \cdot \widetilde{\mathcal{L}}_1 \partial_Z \alpha(T, Z)^* \mathbb{V}_{11}^* e^{-i Q z^*} \, dx dz} \, + $\\
\noindent $\iint {\mathbb{V}^\dagger}^* e^{-iQz^*} \cdot \widetilde{\mathcal{L}}_1 \partial_Z \alpha(T, Z) \mathbb{V}_{11} e^{i Q z} \, dxdz \, + \, \cancel{\iint {\mathbb{V}^\dagger}^* e^{-iQz^*} \cdot \widetilde{\mathcal{L}}_1 \partial_Z \beta(T, Z)^*\mathbb{U}_{11}^* \, dx dz} \, = \, 0$ \\

Where terms with $\beta$ and terms with either $e^{iQz}\cdot e^{iQz}$ or  $e^{-iQz^*}\cdot e^{-iQz^*}$ are zero. Since $\int \limits_{-\pi/Q}^{\pi/Q} \left(e^{iQz}e^{-iQz^*}\right) \, dz \, \ne \, 0$, we have the condition: \\

$\int \limits_{-1}^1 \mathbb{V}^\dagger \cdot \widetilde{\mathcal{L}}_1 \partial_Z \alpha(T, Z)^* \mathbb{V}_{11}^*\, dx \, + \, \int \limits_{-1}^1 {\mathbb{V}^\dagger}^* \cdot \widetilde{\mathcal{L}}_1 \partial_Z \alpha(T, Z) \mathbb{V}_{11} \, dx \, = \, 0$ \\

I believe one can state this as ``$\mathbb{V}^\dagger$ must be orthogonal to $\widetilde{\mathcal{L}}_1 \mathbb{V}_{11}$". Because both $\mathbb{V}^\dagger$ and $\mathbb{V}_{11}$ are even symmetric about x = 0, the requirement is really that $\widetilde{\mathcal{L}}_1 \mathbb{V}_{11}$ is odd symmetric with respect to x, XOR $\partial_Z \alpha(T, Z)$ is odd symmetric with respect to x = 0.
